Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-11-20 analysis/paper/paper.qmd
tukey test result ggplot

#vegetation region#
eco_aov <- aov(min_tcsa ~ as.factor(ecoregion), points_in_veg_zones_all)
summary(eco_aov)
eco_tur<- TukeyHSD(eco_aov)
# plot(eco_tur)

eco_lgm <- round(summary(eco_aov)[[1]][[5]][1], digits = 3)

#eco region#
for_aov <- aov(min_tcsa ~ as.factor(Zone), points_in_veg_zones_forest_box)
summary(for_aov)
for_tur<- TukeyHSD(for_aov)
# plot(for_tur)

for_lgm <- round(summary(for_aov)[[1]][[5]][1], digits = 3)

>>>>

#vegetation region#
points_in_veg_zones_all$ecoregion = as.factor(points_in_veg_zones_all$ecoregion)
eco_aov <- aov(min_tcsa ~ ecoregion, points_in_veg_zones_all)
summary(eco_aov)
eco_tur<- TukeyHSD(eco_aov)
eco_lgm <- round(summary(eco_aov)[[1]][[5]][1], digits = 3)
# plot(eco_tur)
# plot with ggplot
eco_tur_df <- as.data.frame(eco_tur$ecoregion)

ggplot(eco_tur_df, aes(row.names(eco_tur_df))) + 
  geom_boxplot(aes(middle=diff, upper=upr, lower=lwr, ymin=lwr, ymax=upr), stat="identity")

#eco region#
for_aov <- aov(min_tcsa ~ as.factor(Zone), points_in_veg_zones_forest_box)
summary(for_aov)
for_tur<- TukeyHSD(for_aov)
for_lgm <- round(summary(for_aov)[[1]][[5]][1], digits = 3)
# plot(for_tur)
